---
output: 
  html_document:
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
library(dplyr)
library(tidyr)
library(htmltools)

# Load YTD SOT and OTS Master objects
load("C:\\Users\\wenlu\\Documents\\GitHub\\SOTC_OTS_Weekly\\Viz\\SOT_Master_object.rtf")
load("C:\\Users\\wenlu\\Documents\\GitHub\\SOTC_OTS_Weekly\\Viz\\OTS_Master_object.rtf")

fis_yr <- 2017L
brand_vec <- c("GAP NA", "BR NA", "ON NA", "GO NA", "BRFS NA", "GAP INTL", "BR INTL", "ON INTL", "GO INTL", "ATHLETA")

# SOT by brand weekly trend  
SOT_viz_by_brand <- SOT_Master %>%
  filter(FISCAL_YEAR == fis_yr) %>%
  group_by(ReportingBrand, ShipCancelMonth, ShipCancelWeek) %>%
  summarise(TotalUnits= sum(Units), 
            OnTime = sum(Units[Lateness=="OnTime"]), 
            Late = sum(Units[Lateness=="Late"])) %>% 
  ungroup() %>% 
  mutate(SOT = round(OnTime/TotalUnits*100,2)) %>%
  # gather("Lateness", "Units", OnTime:Late) %>%
  droplevels() %>% 
  arrange(ShipCancelWeek)

# SOT_viz_by_brand$Lateness <- as.factor((SOT_viz_by_brand$Lateness))
# SOT_viz_by_brand$Lateness <- factor(SOT_viz_by_brand$Lateness, levels = rev(levels(SOT_viz_by_brand$Lateness)))

SOT <- split(SOT_viz_by_brand, f = SOT_viz_by_brand$ReportingBrand)

OTS_viz_by_brand <- OTS_Master %>%
  group_by(ReportingBrand, Month_Number,Week) %>%
  summarise(TotalUnits= sum(Units), 
            OnTime = sum(Units[Lateness=="OnTime"], na.rm = T), 
            Late = sum(Units[Lateness=="Late"])) %>% 
  ungroup() %>% 
  mutate(OTS = round(OnTime/TotalUnits*100,2)) %>%
  select(ReportingBrand, Month_Number,Week, OTS, TotalUnits, OnTime, Late) %>% 
  # gather("Lateness", "Units", OnTime:Late) %>%
  droplevels() %>% 
  arrange(Week)

OTS <- split(OTS_viz_by_brand, f = OTS_viz_by_brand$ReportingBrand)
# OTS_viz_by_brand$Lateness <- as.factor(OTS_viz_by_brand$Lateness)
# OTS_viz_by_brand$Lateness <- factor(OTS_viz_by_brand$Lateness, levels = rev(levels(OTS_viz_by_brand$Lateness)))
```

### Old Navy North America

Average SOT: `r round(mean(SOT[['ON NA']]$SOT),2)`%  
Highest SOT was `r max(SOT[['ON NA']]$SOT)`% in Week `r SOT[['ON NA']][SOT[['ON NA']]$SOT == max(SOT[['ON NA']]$SOT),]$ShipCancelWeek`  
Lowest SOT was `r min(SOT[['ON NA']]$SOT)`% in Week `r SOT[['ON NA']][SOT[['ON NA']]$SOT == min(SOT[['ON NA']]$SOT),]$ShipCancelWeek`  

Average OTS: `r round(mean(OTS[['ON NA']]$OTS),2)`%  
Highest OTS was `r max(OTS[['ON NA']]$OTS)`% in Week `r OTS[['ON NA']][OTS[['ON NA']]$OTS == max(OTS[['ON NA']]$OTS),]$Week`  
Lowest OTS was `r min(OTS[['ON NA']]$OTS)`% in Week `r OTS[['ON NA']][OTS[['ON NA']]$OTS == min(OTS[['ON NA']]$OTS),]$Week`  

```{r}
p1 <- plot_ly(SOT[['ON NA']]) %>%
  add_trace(x = ~ShipCancelWeek, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
       xaxis = list(title = 'Ship Cancel Week'),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'Old Navy NA Weekly SOT',
       legend =list(x = 1.1, y = 0.9),
       margin = list(t = 120, b = 100))

p2 <- plot_ly(OTS[['ON NA']]) %>%
  add_trace(x = ~Week, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~Week, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~Week, y = ~OTS, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock Week'),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'Old Navy NA Weekly OTS',
         legend =list(x = 1.1, y = 0.9),
         margin = list(t = 120, b = 100))

tagList(
  tags$div(
  style = "display: flex; flex-wrap: wrap",
  tags$div(p1, style = "width: 50%;"),
  tags$div(p2, style = "width: 50%;")
))

```

### Old Navy International

Average SOT: `r round(mean(SOT[['ON INTL']]$SOT),2)`%  
Highest SOT was `r max(SOT[['ON INTL']]$SOT)`% in Week `r SOT[['ON INTL']][SOT[['ON INTL']]$SOT == max(SOT[['ON INTL']]$SOT),]$ShipCancelWeek`  
Lowest SOT was `r min(SOT[['ON INTL']]$SOT)`% in Week `r SOT[['ON INTL']][SOT[['ON INTL']]$SOT == min(SOT[['ON INTL']]$SOT),]$ShipCancelWeek`  

Average OTS: `r round(mean(OTS[['ON INTL']]$OTS),2)`%  
Highest OTS was `r max(OTS[['ON INTL']]$OTS)`% in Week `r OTS[['ON INTL']][OTS[['ON INTL']]$OTS == max(OTS[['ON INTL']]$OTS),]$Week`  
Lowest OTS was `r min(OTS[['ON INTL']]$OTS)`% in Week `r OTS[['ON INTL']][OTS[['ON INTL']]$OTS == min(OTS[['ON INTL']]$OTS),]$Week`  

```{r}
p3 <- plot_ly(subset(SOT_viz_by_brand,ReportingBrand == 'ON INTL')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'Old Navy INTL Weekly SOT',
       legend =list(x = 1.1, y = 0.9),
       margin = list(t = 120, b = 100))


p4 <- plot_ly(subset(OTS_viz_by_brand,ReportingBrand == 'ON INTL')) %>%
  add_trace(x = ~Week, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~Week, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~Week, y = ~OTS, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'Old Navy INTL Weekly OTS',
         legend =list(x = 1.1, y = 0.9),
         margin = list(t = 120, b = 100))

tagList(
  tags$div(
  style = "display: flex; flex-wrap: wrap",
  tags$div(p3, style = "width: 50%;"),
  tags$div(p4, style = "width: 50%;")
))
```


### GAP North America

Average SOT: `r round(mean(SOT[['GAP NA']]$SOT),2)`%  
Highest SOT was `r max(SOT[['GAP NA']]$SOT)`% in Week `r SOT[['GAP NA']][SOT[['GAP NA']]$SOT == max(SOT[['GAP NA']]$SOT),]$ShipCancelWeek`  
Lowest SOT was `r min(SOT[['GAP NA']]$SOT)`% in Week `r SOT[['GAP NA']][SOT[['GAP NA']]$SOT == min(SOT[['GAP NA']]$SOT),]$ShipCancelWeek`  

Average OTS: `r round(mean(OTS[['GAP NA']]$OTS),2)`%  
Highest OTS was `r max(OTS[['GAP NA']]$OTS)`% in Week `r OTS[['GAP NA']][OTS[['GAP NA']]$OTS == max(OTS[['GAP NA']]$OTS),]$Week`  
Lowest OTS was `r min(OTS[['GAP NA']]$OTS)`% in Week `r OTS[['GAP NA']][OTS[['GAP NA']]$OTS == min(OTS[['GAP NA']]$OTS),]$Week`  

```{r}
p5 <- plot_ly(subset(SOT_viz_by_brand,ReportingBrand == 'GAP NA')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'GAP NA Weekly SOT',
       legend =list(x = 1.1, y = 0.9),
       margin = list(t = 120, b = 100))

p6 <- plot_ly(subset(OTS_viz_by_brand,ReportingBrand == 'GAP NA')) %>%
  add_trace(x = ~Week, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~Week, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~Week, y = ~OTS, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'GAP NA Weekly OTS',
         legend =list(x = 1.1, y = 0.9),
         margin = list(t = 120, b = 100))

tagList(
  tags$div(
  style = "display: flex; flex-wrap: wrap",
  tags$div(p5, style = "width: 50%;"),
  tags$div(p6, style = "width: 50%;")

))

```


### GAP International

Average SOT: `r round(mean(SOT[['GAP INTL']]$SOT),2)`%  
Highest SOT was `r max(SOT[['GAP INTL']]$SOT)`% in Week `r SOT[['GAP INTL']][SOT[['GAP INTL']]$SOT == max(SOT[['GAP INTL']]$SOT),]$ShipCancelWeek`  
Lowest SOT was `r min(SOT[['GAP INTL']]$SOT)`% in Week `r SOT[['GAP INTL']][SOT[['GAP INTL']]$SOT == min(SOT[['GAP INTL']]$SOT),]$ShipCancelWeek`  

Average OTS: `r round(mean(OTS[['GAP INTL']]$OTS),2)`%  
Highest OTS was `r max(OTS[['GAP INTL']]$OTS)`% in Week `r OTS[['GAP INTL']][OTS[['GAP INTL']]$OTS == max(OTS[['GAP INTL']]$OTS),]$Week`  
Lowest OTS was `r min(OTS[['GAP INTL']]$OTS)`% in Week `r OTS[['GAP INTL']][OTS[['GAP INTL']]$OTS == min(OTS[['GAP INTL']]$OTS),]$Week`

```{r}
p7 <- plot_ly(subset(SOT_viz_by_brand,ReportingBrand == 'GAP INTL')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~ShipCancelWeek, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'GAP INTL Weekly SOT',
       legend =list(x = 1.1, y = 0.9),
       margin = list(t = 120, b = 100))


p8 <- plot_ly(subset(OTS_viz_by_brand,ReportingBrand == 'GAP INTL')) %>%
  add_trace(x = ~Week, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~Week, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~Week, y = ~OTS, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'GAP INTL Weekly OTS',
         legend =list(x = 1.1, y = 0.9),
         margin = list(t = 120, b = 100))

tagList(
  tags$div(
  style = "display: flex; flex-wrap: wrap",
  tags$div(p7, style = "width: 50%;"),
  tags$div(p8, style = "width: 50%;")

))
```


