---
title: "Shipped On Time to Contract / On Time To Stock Weekly Trend"
output: 
  flexdashboard::flex_dashboard:
    orientation: row
    vertical_layout: scroll
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flexdashboard)
library(plotly)
library(dplyr)
library(tidyr)
library(htmltools)
library(knitr)

# Load YTD SOT and OTS Master objects
load("C:\\Users\\wenlu\\Documents\\SOTC-OTS\\Week 2\\.RData")

f1 <- list(
  
  size = 10,
  color = "black"
)
```

Data as of `r SOT_Data_Pulled`

Gap Inc
=======================================================================
Row
-----------------------------------------------------------------------
### Gap Inc SOTC Weekly

```{r}
plot_ly(SOT_GapInc) %>% 
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
       xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'Gap Inc Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))

```

Row
-----------------------------------------------------------------------
### Gap Inc OTS Weekly

```{r}
plot_ly(OTS_GapInc) %>% 
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'Gap Inc Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

Old Navy
=======================================================================
Row
-----------------------------------------------------------------------
### Old Navy North America SOTC Weekly

```{r}
plot_ly(SOT[['ON NA']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
       xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'Old Navy NA Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

### Old Navy North America OTS Weekly

```{r}
plot_ly(OTS[['ON NA']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'Old Navy NA Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

Row
-----------------------------------------------------------------------
### Old Navy International SOTC Weekly

```{r}
plot_ly(subset(SOT_viz_by_brand,ReportingBrand == 'ON INTL')) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
       xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'Old Navy INTL Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
       margin = list(t = 105, b = 105))
```

### Old Navy International OTS Weekly
```{r}
plot_ly(subset(OTS_viz_by_brand,ReportingBrand == 'ON INTL')) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'Old Navy INTL Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

GAP
=======================================================================

Row
-----------------------------------------------------------------------

### GAP North America SOTC Weekly

```{r}
plot_ly(subset(SOT_viz_by_brand,ReportingBrand == 'GAP NA')) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'GAP NA Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))

```

### GAP North America OTS Weekly

```{r}
plot_ly(subset(OTS_viz_by_brand,ReportingBrand == 'GAP NA')) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'GAP NA Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

Row
-----------------------------------------------------------------------
### GAP International SOTC Weekly

```{r}
plot_ly(subset(SOT_viz_by_brand,ReportingBrand == 'GAP INTL')) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'GAP INTL Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

### GAP International SOTC Weekly

```{r}
plot_ly(subset(OTS_viz_by_brand,ReportingBrand == 'GAP INTL')) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'GAP INTL Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

Row
-----------------------------------------------------------------------
### Gap Outlet North America SOTC Weekly

```{r}
plot_ly(SOT[['GO NA']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'GO NA Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

### Gap Outlet North America OTS Weekly

```{r}
plot_ly(OTS[['GO NA']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'GO NA Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

Row
-----------------------------------------------------------------------
### Gap Outlet International SOTC Weekly

```{r}
plot_ly(SOT[['GO INTL']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'GO INTL Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))



```

### Gap Outlet International OTS Weekly

```{r}
plot_ly(OTS[['GO INTL']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'GO INTL Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

Banana Republic
=======================================================================
Row
-----------------------------------------------------------------------

### Banana Republic North America SOTC Weekly

```{r}
plot_ly(SOT[['BR NA']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'BR NA Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

### Banana Republic North America OTS Weekly

```{r}
plot_ly(OTS[['BR NA']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'BR NA Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))

```

Row
-----------------------------------------------------------------------
### Banana Republic International SOTC Weekly

```{r}
plot_ly(SOT[['BR INTL']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'BR INTL Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

### Banana Republic International OTS Weekly

```{r}
plot_ly(OTS[['BR INTL']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'BR INTL Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

Row
-----------------------------------------------------------------------
### BRFS North America SOTC Weekly

```{r}
plot_ly(SOT[['BRFS NA']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'BRFS NA Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

### BRFS North America OTS Weekly

```{r}
plot_ly(OTS[['BRFS NA']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'BRFS NA Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```


Athleta
=======================================================================
Row
-----------------------------------------------------------------------

### Athleta SOTC Weekly

```{r}
plot_ly(SOT[['ATHLETA']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~SOT, type = 'scatter', mode = 'lines', name = 'SOT (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Ship Cancel (YY-WW)',
                    tickangle = 45,
                    tickfont = f1),
       yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                     hoverformat ='.3s'),
       yaxis2  = list(side = 'right',overlaying = "y"),
       title = 'Athleta Weekly Shipped On Time to Contract',
       legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

### Athleta OTS Weekly

```{r}
plot_ly(OTS[['ATHLETA']]) %>%
  add_trace(x = ~YearWk, y = ~OnTime, type = 'bar', name = 'OnTime', xaxis = 'x1',
            marker = list(color = '#4c8dd9')) %>%
  add_trace(x = ~YearWk, y = ~Late, type = 'bar', name = 'Late', xaxis = 'x1',
            marker = list(color ='#fc9d74')) %>%
  add_trace(x = ~YearWk, y = ~OTS, type = 'scatter', mode = 'lines', name = 'OTS (%)', yaxis = 'y2',
            line = list(color = '#5fd4b1', width = 2.5)) %>%
  layout(barmode = 'stack',
         xaxis = list(title = 'Planned Stock (YY-WW)',
                      tickangle = 45,
                      tickfont = f1),
         yaxis  = list(title = 'Units', side = 'left', showgrid = FALSE, zeroline = FALSE,
                       hoverformat ='.3s'),
         yaxis2  = list(side = 'right',overlaying = "y"),
         title = 'Athleta Weekly On Time to Stock',
         legend =list(x = 1.05, y = 0.9),
         margin = list(t = 105, b = 105))
```

